Reference model in feature selection problems \vspace{.1in}

### 2019-05-21 paper/ref_approach.tex
more in the introduction and added hyperparameter info DL RHS

Regardless which kind of selection problem we are trying to solve, we consider examples of the reference model approach all those methods that make use of a full-encompassing model, i.e. the reference one, to carry out the selection. The idea of using a reference model is already present in some works from the 60s as \cite{paper:reference_lindley}. It is also the basis for the projection predictive approach \citep{paper:original_proj, paper:projpred}, from which we have taken the hint of using the reference model as a filter (see Section \ref{reference-model-approach}).

\begin{itemize}
\item add original contribution that are:
\item motivation and example on how the use of a reference model improves the selection (projpred example)
\item a comparison between using a reference model or not in the normal means problem  both with simulated data and the bodyfat data
\end{itemize}

@@

\hypertarget{simulated-data}{%
\subsection{Simulated data}\label{simulated-data}}
\begin{itemize}
\item details about hyperparameters of the methods used
\end{itemize}

@@

\hypertarget{shrinkage-signal}{%
\subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
In the framework of full-Bayes methods we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}. Although the horseshoe+ prior by \cite{paper:horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection. 
As already mentioned, continuous priors do not usually give an automatic selection procedure, in this Section we study the amount of shrinkage and the bias of the posterior median looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}). In the case of the regularised horseshoe prior, we also take into account the posterior mean for the shrinkage factor for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} is defined as:
\
\begin{equation}
\kappa_{j}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}
\end{equation}
with $\tau$ and $\lambda_{j}$ respectively global and local shrinkage parameters, for further details see \cite{paper:rhs}.

>>>>

Regardless which kind of selection problem we are trying to solve, we consider examples of the reference model approach all those methods that make use of a full-encompassing model, i.e. the reference one, to carry out the selection. The idea of using a reference model is already present in some works from the 60s as \cite{paper:reference_lindley}. It is also the basis for the projection predictive approach \citep{paper:original_proj, paper:projpred}, from which we have taken the hint of using the reference model as a filter (see Section \ref{reference-model-approach}). The reference model, if properly designed, is a less noisy representation of the true data generation mechanism with respect to the observed data distribution. Therefore in a variable selection context it improves the selection process in terms of quality and stability of the selected subset of features, whether the goal is the smallest model with high enough predictive performance or the whole subset of relevant features.

In this paper we try to show such benefits with:

\begin{itemize}
\item a real-world data example comparing the projection predictive approach with the stepwise backward regression selection,
\item a structured comparison in the framework of the normal means estimation problem using different state-of-the-art methods with or not a reference model on top of the procedure, with simulated data and a real-world data example.
\end{itemize}

@@

\hypertarget{simulated-data}{%
\subsection{Simulated data}\label{simulated-data}}

@@

\hypertarget{shrinkage-signal}{%
\subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
In the framework of full-Bayes methods we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}. Although the horseshoe+ prior by \cite{paper:horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection. We used an uniform prior on $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs} setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage.

As already mentioned, continuous priors do not usually give an automatic selection procedure, in this Section we study the amount of shrinkage and the bias of the posterior median looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}). In the case of the regularised horseshoe prior, we also take into account the posterior mean for the shrinkage factor for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} is defined as:
\
\begin{equation}
\kappa_{j}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}
\end{equation}
with $\tau$ and $\lambda_{j}$ respectively global and local shrinkage parameters, for further details see \cite{paper:rhs}.
